Giant Low Surface Brightness Galaxies as Merger Remnants

### 2015-04-13 glsb.tex
edits

Both our objects have been observed with SDSS, making it possible to compare them to a large number of systems.  The outer disks of GLSBs are faint enough that the SDSS photometric pipeline effectively ignores them.

To make a comparison sample of galaxies from SDSS, we select galaxies with redshifts between 0.01 and 0.07 and de-reddned $r$ magnitude between 13.5 and 17.7.  When comparing to just elliptical galaxies we make the additional color-cut of $u-r > 2.1$ (and some morphology selectors).  These are simply galaxies for comparison, not a rigorously defined volume-complete sample.  Our full SQL querries are shown in \S\ref{SQL}.  This gives us a sample of 141,001 objects, 45,703 of which have red colors.  Throughout, we use the CosmoloPy\footnote{\url{http://roban.github.com/CosmoloPy/}} fiducial cosmology ($h=0.704$, $\Omega_{m_0}=0.2726$, $\Omega_{\lambda_0}=0.7274$).

@@

Figure~\ref{elliptical_relations} shows where the GLSBs fall on the major galaxy relations.  We use extinction corrected magnitudes and $k$-corrected colors\citep{Chilingarian10}.  Both of our GLSBs lie on the red-sequence in a color-magnitude diagram.

The central regions of GLSBs are often called ``bulges'', however, looking at Figure~\ref{elliptical_relations}, it is clear that these are much brighter than bulges of typical spiral galaxies and the GLSBs are on the bright end of the red-sequence.

@@

%Note that we are not correcting for Malmquist bias or biases in the SDSS spectroscopic selection criteria.  Our selection is simply for galaxies of a similar magnitude and redshift.

@@

XXX-crap, whatever happened to the gas kinematics?  There are emission lines out there--are they bright enough to get in single fibers of not?  Looks like for Malin 2 the emission lines are only coming from one side of the galaxy.  UGC 6614 is mostly emission from the center.

@@

>>>>

Both of our objects have been observed with SDSS, making it possible to compare them to a large number of systems.  The outer disks of GLSBs are faint enough that the SDSS photometric pipeline effectively ignores them.

To make a comparison sample of galaxies from SDSS, we select galaxies with redshifts between 0.01 and 0.07 and de-reddned $r$ magnitude between 13.5 and 17.7.  When comparing to just elliptical galaxies we make the additional color-cut of $u-r > 2.1$ (and some morphology selectors).  These are simply galaxies for comparison, not a rigorously defined volume-complete sample.  Our full SQL querries are shown in \S\ref{SQL}.  This gives us a sample of 141,001 objects, 45,703 of which have red colors.  Throughout, we use the CosmoloPy\footnote{\url{http://roban.github.com/CosmoloPy/}} fiducial cosmology ($h=0.704$, $\Omega_{m_0}=0.2726$, $\Omega_{\lambda_0}=0.7274$).  Note that we are not correcting for Malmquist bias or biases in the SDSS spectroscopic selection criteria.  Our selection is simply for galaxies of a similar magnitude and redshift.

@@

Figure~\ref{elliptical_relations} shows where the GLSBs fall on the major galaxy relations.  We use extinction corrected magnitudes and $k$-corrected colors\citep{Chilingarian10}.  Both of our GLSBs lie on the red-sequence in the color-magnitude diagram.

The central regions of GLSBs are often called ``bulges'', however, looking at Figure~\ref{elliptical_relations}, it is clear that these are much brighter than bulges of typical spiral galaxies and the centers of GLSBs are on the bright end of the red-sequence.

@@

@@

%XXX-crap, whatever happened to the gas kinematics?  There are emission lines out there--are they bright enough to get in single fibers of not?  Looks like for Malin 2 the emission lines are only coming from one side of the galaxy.  UGC 6614 is mostly emission from the center.

@@

XXX--We are currently observing higher spatial resolution IFU data with Gemini (GN-2015A-Q-75) of the central region of these galaxies to confim they are normal elliptical galaxies and to help constrain a more sophisticated dynamical model.
